The Name of the Title is Hope

### 2024-04-03 input/7_discussion.tex
UIST submission

\section{Discussion}
With this paper, we contributed a new way to design the experience of action augmentation augmented experiences with the potential to maintain a user's SoA: a BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11.5 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of .7. We demonstrated in eight participants that one effect of SoA, intentional binding, is maintained when using our system. However, the subjectively rated level of control was lower when using the system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

Our system was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all technical devices to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 Euros. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density coverage of about 12 channels on average for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' tendency for temporal binding when comparing the three experimental conditions. We conclude that taking users' sentiments and ratings of control into account, this indicates a general modulation of agency for our intention-based augmentation. We believe this to be a very promising finding because our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

@@

However, we learned from these paradigms that increasing participants' reaction times by about 80 ms is optimal with regards to maintaining SoA~\cite{Kasahara2019-sk}. On one hand, our system is capable of delivering pre-emption within this `SoA-optimal' time range. On the other hand, however, the performance of the sub-optimal performance of the classifier means a lot of variation due to false positive detections. While in some cases, as we observed in the users' comments, the stimulation may have pre-empted a user's motion, false positive stimulation may have had a significant impact on the overall impression of the system, see section~\ref{improving_classifier} below.

@@

For the current study, we must note the following limitations arising from the (potentially) insufficient performance of the classification system. To provide a full picture we first describe the impact from a signal detection point of view: False negative classifications meant that the system did not trigger an EMS pulse in line with participants intent to tap on the screen. On the other hand, false positive classification meant that an EMS pulse was sent in the absence of a true intention by the participant. Both cases, individually and jointly, had the potential to significantly impact the user experience and erode trust in the system. In the interviews, participants reported only a relatively low number of correctly detected intentions. This may have ultimately led to a misalignment between users' perceptions and the observed, measurable, system behavior.

As a consequence, the insights gained into the system's potential to preserve a sense of agency are limited. The quantitative metrics employed in our study, specifically those measuring the sense of control (including temporal binding and item assessment), may not have captured the nuanced temporal alignment experiences associated with EMS augmentation and user movement intentions but rather a more holistic assessment of the entire experimental block, which included trials with missed stimulation, too early stimulation, and some trials where the stimulation was in alignment with the participants' intent.

>>>>

\section{Discussion}
With this paper, we contributed a new way to design the experience of action augmentation with the potential to maintain a user's SoA: A BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of about .7. We demonstrated in ten participants that one effect of SoA, intentional binding, is maintained when using our system. However, the subjectively rated level of control was lower when using the system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

Our system was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all technical devices to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 Euros. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density channel coverage for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' tendency for temporal binding when comparing the three experimental conditions.

We first conclude that augmentation generally impacted SoA as was evident in the users' sentiments and ratings of control. While we believe that our prototype did not perform at a consistently high enough performance to allow for more fine-grained inferences about the the pre-emptive gain it achieved, we maintain that in some cases it elicited an pre-emptiot that maintained agency to a certain degree. We believe this to be a very promising finding because our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

@@

However, we learned from these paradigms that increasing participants' reaction times by about 80 ms is optimal with regards to maintaining SoA~\cite{Kasahara2019-sk}. On one hand, our system is capable of delivering pre-emption within this `SoA-optimal' time range. On the other hand, however, the sub-optimal performance of the classifier resulted in a lot of variation due to false positive detections. While in some cases, as we observed in the users' comments, the stimulation may have pre-empted a user's motion, false positive stimulation may have had a significant impact on the overall impression of the system, see section~\ref{improving_classifier} below.

@@

For the current study, we must note the following limitations arising from the (potentially) insufficient performance of the classification system. To provide a full picture we first describe the impact from a signal detection point of view: False negative classifications meant that the system did not trigger an EMS pulse in line with participants intent to tap on the screen. On the other hand, false positive classification meant that an EMS pulse was sent in the absence of a true intention by the participant. Both cases, individually and jointly, had the potential to impact the user experience and erode trust in the system. In the interviews, participants reported only a relatively low number of correctly detected intentions. This may have ultimately led to a misalignment between users' perceptions and the observed, measurable, system behavior. Furthermore, the necessity for a fixed block/condition order may have further contributed to this effect. However, keeping the order was necessary in order to first obtain training data for the BCI based on the unique EEG signals of each participant.

As a consequence, the insights gained into the system's potential to preserve a sense of agency are limited. The quantitative metrics employed in our study, specifically those measuring the sense of control (including temporal binding and item assessment), may not have captured the nuanced temporal alignment experiences associated with EMS augmentation and user movement intentions but rather a more holistic assessment of the entire experimental block, which included trials with missed stimulations, too early stimulations, and some trials where the stimulation was in alignment with the participants' intent.
